Manuscript title here

### 2021-04-27 doc/ms/ms.Rmd
updated analysis and ms

To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
hierarchical multivariate model [@fordyce2011]. Here, the diet of a consumer population, *i*, is a multinomial vector,$\overrightarrow{y_i}$, of
$$\overrightarrow{y_i} \sim Multinomial(\overrightarrow{p_i}, n_i)$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value. **add in
site-level model parameter and model fitting language**. Models were fit in Stan with the 'brms' package in R [@burkner2017]. For non-dominant taxa, diet proportions were imputed
from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing
values.

@@

Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
diet proportions, diet-specific assimilation efficiencies, $AE_{i}$, and assumed net production efficiencies, $NPE$, to estimate consumption of organic matter. For each food
category, $\textit{i}$, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food
category. The relative production from each food type was then multiplied by the interval-level production and finally divided by $GGE_{i}$ to estimate consumption of organic
matter from each food category by a consumer [@benke1980]. Consumption was calculated for each taxon across sampling intervals (typically \~1 month). Total interval consumption was
calculated by summing across all taxa, while annual consumption was calculated by summing across all taxa and intervals. Variability in consumption estimates was estimated through
a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with
the TBP method using simulated diet proportions (see *Diet analysis* above), diet-specific assimilation efficiencies, and net production efficiency. Variability in $AE_{i}$ was
incoporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36),
filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants
(bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997]. Variability in $NPE$ was
incorporated by resampling values from an assumed beta distribution with median $NPE$ = 0.45 (95% PI = 0.4-0.5). Beta distributions were fit using the 'get.beta.par()' function
within the *rriskDistributions* package [@belgorodski2017].

@@

Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020].Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature. Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$.

@@

diet_predictions_item = modeled_diets[["diet_predictions"]] %>%
   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
    group_by(diet_item) %>%
    dplyr::summarise(across(rel_area, list(mean = ~mean(.x, na.rm = TRUE),
                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))
```

Patterns of OM flux among streams were most closely tied to total energy demands as consumer diets exhibited high similarity among streams (Figure SX). Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% round(1)`]). Calculated percent similarity among streams ranged from XX to XX and showed no relationship with mean stream temperature.

@@

n_dom_min = spp_dominance %>% dplyr::slice(which.min(n_dom))
n_dom_max = spp_dominance %>% dplyr::slice(which.max(n_dom))

@@

## Trait distributions among sites and taxa

@@

pb_summ = skew_analysis[["PB_skew_summ"]]

m_summ = skew_analysis[["M_skew_summ"]]
```

The fluxes of OM were distributed differently across body sizes and turnover rates (**P:B**) among and within streams. Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2). Fluxes were skewed differentially towards larger body sizes (positive skew) among streams, with skew estimates with body size (**M**) ranging from `r m_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3). Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean)%>% round(2)` to `r pb_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).

When compared to random

-- mean skew with M ranged from

-- The probability of observing these values of skew with pb `r pb_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`

-- The probability of observing these values of skew with M `r m_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`

>>>>

To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
hierarchical multivariate model [@fordyce2011, @coblentz2017]. Here, the diet of a consumer population, *i*, is a multinomial vector,$\overrightarrow{y_i}$, of
$$\overrightarrow{y_i} \sim Multinomial(\overrightarrow{p_i}, n_i)$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value. **add in
site-level model parameter and model fitting language** . Models were fit in Stan with the 'brms' package in R [@burkner2017]. For non-dominant taxa, diet proportions were imputed
from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing
values.

From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities [*PS*; @whittaker1952] among modeled diet estimates (proportional similarity estimates from empirical diets give similar results to modeled estimates; Supporting Materials). Proportional similarities were calculated as:

$$ PS = 1 - 0.5 \sum_{j=1}^S|p_{x,i} - p_{y,i}|$$

where, *p~x,i~* is the proportion of food resource *i* in the diet of taxon *x*, *p~y,i~* is the proportion of food resource *i* in the diet of taxon *y*, and there are *S* food categories. Proportional similarity was calculated across all taxa within a stream based on modeled diet contributions from each taxon. To calculate *PS* among streams we sampled 1000 estimates of the mean stream-level diet proportions for each stream and calculated *PS* for each.

@@

Consumption fluxes (g m^-2^ t^-1^) were calculated using the trophic basis of production method (TBP; [@benke1980]. Taxon-specific secondary production estimates were combined with
diet proportions, diet-specific assimilation efficiencies, *AE~i~*, and assumed net production efficiencies, *NPE*, to estimate consumption of organic matter. For each food
category, *i*, diet proportions were multiplied by the gross growth efficiency ($GGE_{i} = AE_{i} * NPE$) to calculate the relative production attributable to each food
category. The relative production from each food type was then multiplied by the interval-level production and finally divided by $GGE_{i}$ to estimate consumption of organic
matter from each food category by a consumer [@benke1980]. Consumption was calculated for each taxon across sampling intervals (typically \~1 month). Total interval consumption was
calculated by summing across all taxa, while annual consumption was calculated by summing across all taxa and intervals. Variability in consumption estimates was estimated through
a Monte Carlo approach, wherein bootstrapped vectors of secondary production for each taxon (see *Secondary production* methods above) were resampled and consumption estimated with
the TBP method using modeled diet proportions (see *Diet analysis* above), diet-specific assimilation efficiencies, and net production efficiency. Variability in *AE~i~* was
incorporated by resampling values from beta distributions fit to median and 2.5% and 97.5% percentiles for each diet item: diatoms = 0.30 (95% percentile interval (PI): 0.24-0.36),
filamentous and green algae = 0.30 (95% PI: 0.24-0.36), cyanobacteria = 0.10 (95% PI: 0.08-0.12), amorphous detritus = 0.10 (95% PI: 0.08-0.12), vascular and non-vascular plants
(bryophytes) = 0.1 (95% PI:: 0.08-0.12), and animal material = 0.7 (95% PI: 0.56-0.84)[@welch1968; @cross2007; @cross2011; @benke1980; @benke1997]. Variability in *NPE* was
incorporated by resampling values from an assumed beta distribution with median *NPE* = 0.45 (95% PI = 0.4-0.5). Beta distributions were fit using the 'get.beta.par()' function
within the *rriskDistributions* package [@belgorodski2017].

@@

Annual community energy demand mirrored patterns of secondary production previously reported [@junker2020]. Community energy demand varied ~`r round((max_demand$flux_mg_m_y_mean/min_demand$flux_mg_m_y_mean),1)`-fold across streams (`r round((min_demand$flux_mg_m_y_mean/1000), 3)`[`r round((min_demand$flux_mg_m_y_quant2.5/1000),3)` , `r round((min_demand$flux_mg_m_y_quant97.5/1000),3)`] to `r round((max_demand$flux_mg_m_y_mean/1000),1)` [`r round((max_demand$flux_mg_m_y_quant2.5/1000),1)` , `r round((max_demand$flux_mg_m_y_quant97.5/1000),1)`]; g AFDM $m^{-2} y^{-1}$ mean [95% percentile interval (PI)]) and was positively related to temperature. Total OM flux through the consumer community was strongly associated with community energy demand and varied from `r round((min_flux$flux_mg_m_y_mean/1000),1)` [`r round((min_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((min_flux$flux_mg_m_y_quant97.5/1000),1)`] to `r round((max_flux$flux_mg_m_y_mean/1000),1)`[`r round((max_flux$flux_mg_m_y_quant2.5/1000),1)`,`r round((max_flux$flux_mg_m_y_quant97.5/1000),1)`] g AFDM $m^{-2} y^{-1}$.

@@

diet_predictions_item = modeled_diets[["diet_predictions"]] %>%
   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
    group_by(diet_item) %>%
    dplyr::summarise(across(rel_area, list(mean = ~mean(.x, na.rm = TRUE),
                                                            quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
                                                            quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
                                                            quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
                                                            quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
                                                            quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))

drake::loadd(diet_similarity)
min_within_overlap = diet_similarity[['within_overlap_summ']] %>% dplyr::slice_min(meanoverlap_mean)
max_within_overlap = diet_similarity[['within_overlap_summ']] %>% dplyr::slice_max(meanoverlap_mean)

# min_among_overlap = diet_similarity[[]]

among_overlap_mean = mean(diet_similarity[['among_overlap_mean']], na.rm = TRUE)
among_overlap_quant2.5 = quantile(diet_similarity[['among_overlap_mean']], 0.025, na.rm = TRUE)
among_overlap_quant97.5 = quantile(diet_similarity[['among_overlap_mean']], 0.975, na.rm = TRUE)

Patterns of OM flux among streams were most closely tied to total consumer energy demands as consumer diets exhibited high similarity among streams (Figure SX). Diets composition among all streams were dominated by diatoms (`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "diatom") %>% select(contains('quant97.5')) %>% round(1)`]), amorphous detritus (`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "amorphous_detritus") %>% select(contains('quant97.5')) %>% round(1)`]), and green algae (`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('mean')) %>% round(1)`% [`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant2.5')) %>% round(1)`,`r diet_predictions_item %>% dplyr::filter(diet_item == "green_algae") %>% select(contains('quant97.5')) %>% round(1)`]). Within streams, diet similarity ranged from `r min_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(min_within_overlap$meanoverlap_quant2.5,2)` -- `r round(min_within_overlap$meanoverlap_quant97.5,2)`) to `r max_within_overlap %>% dplyr::select(meanoverlap_mean) %>% round(2)` (`r round(max_within_overlap$meanoverlap_quant2.5,2)` -- `r round(max_within_overlap$meanoverlap_quant97.5,2)`). Among streams, diet overlap was similarly high and mean overlap among all streams was `r round(among_overlap_mean,2)`% (`r round(among_overlap_quant2.5,2)` -- `r round(among_overlap_quant97.5,2)` 95% PI). Diet similarity of pairwise comparisons among streams showed Pairwise comparisons among streams calculated percent similarity among streams ranged from XX to XX and showed no relationship with mean stream temperature.

@@

n_dom_min = spp_dominance %>% dplyr::slice_min(n_dom)
n_dom_max = spp_dominance %>% dplyr::slice_max(n_dom)

@@

## OM fluxes along species trait distributions among sites and taxa

@@

pb_skew_summ = skew_analysis[["PB_skew_summ"]]

m_skew_summ = skew_analysis[["M_skew_summ"]]
```

The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams. Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2). Fluxes were skewed differentially towards larger body sizes (positive skew) or towards smaller body sizes (negative skew) among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` (Figure 3). Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean)%>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).

When compared to a random ordering while also preserving the relative distribution of fluxes among taxa, the probability of observing a similar or more extreme skew of within stream OM fluxes in relation to species body size ranged from `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% min%>% round(2)` to `r m_skew_summ %>% select(matches("M.*prob_mean")) %>% max%>% round(2)`. Similarly, the probability of a more extremely skewed distribution in relation to population biomass turnover ranged from `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% min%>% round(2)` to `r pb_skew_summ %>% select(matches("pb.*prob_mean")) %>% max%>% round(2)`.

### 2021-04-27 doc/ms/tables-figures.Rmd
updated analysis and ms

Figure 2. Evenness profiles of species' relatives fluxes among streams.

```{r evenness profile, echo=FALSE, warning=FALSE, message=FALSE,  fig.width=5, fig.height=5, dpi = 450}
loadd(hill_diversity_analysis)
hill_diversity_analysis

@@

Figure S1. Modeled diet proportions among streams

>>>>

<!-- \newpage -->

<!-- Figure 2. Evenness profiles of species' relatives fluxes among streams. -->

<!-- ```{r evenness profile, echo=FALSE, warning=FALSE, message=FALSE,  fig.width=5, fig.height=5, dpi = 450} -->
<!-- loadd(hill_diversity_analysis) -->
<!-- hill_diversity_analysis -->

<!-- ``` -->

@@

Figure 4. Bootstrapped distribution of skew statistics from OM fluxes with body size, *M*, and (b) population annual production:biomass ratio relative to the distribution of skew statistics of 100,000 random orderings.

```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE}
drake::loadd(random_skew_fig)
grid.draw(random_skew_fig)

\newpage
Figure S1. Modeled diet proportions among streams
